---
title: "PA1_template.Rmd"
author: "Armand"
date: "Monday, November 17, 2014"
output: html_document
---


#Loading and preprocessing the data

. load and processing data

```{r}
library(plyr)
data<-read.csv("activity.csv", sep=",", header=TRUE)
step<- data[!is.na(data$steps),]
totalsteps<-ddply(step, .(date), summarize, total=sum(steps))
```

. plot data

```{r}
hist(totalsteps$total, xlab="Total steps per day",col="navy", main=" Histogram of total steps taken per day" )
```

. Calculate and report the mean and median total number of steps taken per day

```{r}
smean<-mean(totalsteps$total)
smedia<-median(totalsteps$total)
```



# What is the average daily activity pattern?

.Make a time series plot (i.e. type = ???l???) of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r}
intervalsteps<-ddply(step, .(interval), summarize, total=mean(steps))
plot(intervalsteps$interval,intervalsteps$total, type="l" ,xlab="Time Interval (5 min)", ylab=" Mean Steps per day", main ="Average steps taken in 5 min Interval", col="green")

```


.Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps? 

```{r}

max<-intervalsteps[which.max(intervalsteps$total),1]
```

# Imputing missing values

.Calculate and report the total number of missing values in the dataset (i .e. the total number of rows with NAs)

```{r}

nas<-sum(is.na(data$steps))
  
```

.Devise a strategy for filling in all of the missing values in the dataset. The strategy does not need to be sophisticated. For example, you could use the mean/median for that day, or the mean for that 5-minute interval, etc.

```{r}
data2<-data

index1<-(which(is.na(data$steps)))


 for(index in index1) {
    
    data2$steps[index]<- intervalsteps[intervalsteps$interval == data2$interval[index], ]$total
    
}


totalsteps2<-ddply(data2, .(date), summarize, total=sum(steps))

  
```


. Make a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day. 


```{r}
hist(totalsteps$total, xlab="Total steps per day",col="magenta", main=" Histogram of total steps taken per day with NA filled" )

smean2<-mean(totalsteps2$total)
smedia2<-median(totalsteps2$total)
  
```









